---
title: "ColorBrewerLab3"
author: "Katelyn Diaz"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(RColorBrewer)
glimpse(ToothGrowth)
library(nasaweather)
library(ggthemes)

# summary(ToothGrowth)
display.brewer.all()


```

### Exercise 1:
##### Make a boxplot of the ToothGrowth data, with x = dose, y = len, and fill = dose. Store it in a variable called my_plot.


```{r message = FALSE,  }
# Insert code for Exercise 1 here

ToothGrowth <- ToothGrowth %>%
  mutate (dose = factor(dose))
summary(ToothGrowth)


my_plot <- ggplot(data = (ToothGrowth), aes(x=dose, y=len, fill =dose)) +
  geom_boxplot()

my_plot +
  scale_fill_manual(values = c("#004f71", "#465a01", "#981d97"))

```


### Exercise 2: 
##### Try out a few other color palettes
```{r message = FALSE,  }
ToothGrowth <- ToothGrowth %>%
  mutate (dose = factor(dose))
summary(ToothGrowth)


my_plot <- ggplot(data = (ToothGrowth), aes(x=dose, y=len, fill =dose)) +
  geom_boxplot()

my_plot +
  scale_fill_brewer(palette = "Set2")

my_plot +
  scale_fill_brewer(palette = "Oranges")

my_plot +
  scale_fill_brewer(palette = "BrBG")

```
Exercise 3: Install the nasaweather package and load it

### Exercise 4:
##### Plot the storms in my_storms, mapping horizontal position to longitude, vertical position to latitude, and color to wind speed. Also use a facet_wrap() to make small multiples according to the name of each storm.

```{r message = FALSE,  }
my_storms <- storms %>%
    filter(year == 1995)

my_storms <- ggplot(data = my_storms, aes(group = name, x=long, y=lat, color = wind)) +
  geom_line()

my_storms +
  facet_wrap(~name) +
  scale_fill_distiller(palette = "Blues")
# when to use color filler vs distiller?
# didn't display color as geom_boxplot
```

### Exercise 5:
##### Do you think a sequential or diverging color scheme is most appropriate for wind speed? Justify your answer.
  A sequential color scheme is just hues of the same color, while diverging are different colors. I believe sequential would be more appropriate because it is talking about one thing, and moves in one direction of total speed (you can't have negative wind strength).


```{r message = FALSE,  }
glimpse(ChickWeight)
cute_chick <- ChickWeight 

cute_chick <- ggplot(data = cute_chick, aes(group = Diet, x=Chick, y=weight, color = Diet)) +
  ggtitle("Chicken weight depending on diet type") +
  ylab("Weight of Chick") +
  
  geom_boxplot()

cute_chick +
  scale_fill_distiller(palette = "Blues")


   

```


```{r message = FALSE,  }
glimpse(ChickWeight)
```
...

